MultiDataImportPico

### 2023-12-08 Code/MultiDataImportPico.Rmd
Edit annotations
Removed Googlesheet and GoogleDrive libraries

# To Do

-move filter for negative OD to point of log curve fitting Filtering
negative points needed for current noise filtering, so placed just
before noise filtering; with more sophisticated noise filtering

@@

# Load Libraries
```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)
library(photobiologyWavebands)

@@

#set Photobiology colors
```{r set colours}
MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"

>>>>

@@

# Load Libraries
```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(photobiologyWavebands)

@@

#set Photobiology colors
```{r set colours}
MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
